### 2016-10-06 Manuscript/SW_early_life_telomeres_tables_and_figures.Rmd
Home edits

temp <- subset(dd,LayYear>1995)

@@

Fig2x <- ggplot(temp,aes(x = CatchYear,y = RTL))+
  ylab('RTL') + 
  xlab('Cohort') +
  theme_classic() +
  theme(axis.text.x = element_text(size = 12,angle = 90), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
                axis.line.x = element_line(colour = 'black'),
        axis.line.y = element_line(colour = 'black'),
        legend.position = 'top')+
  geom_boxplot(aes(group = CatchYear),outlier.colour = 'grey',notch=F,alpha=0)+
  geom_smooth()

@@

temp <- dd
temp$LogAge <- log(temp$Agemonths+1)

temp2 <- subset(temp,CatchYear<2014)

temp2$cenTL <- (temp2$RTL-tapply(temp2$RTL,temp2$Agemonths,mean)[as.character(temp2$Agemonths)])/tapply(temp2$RTL,temp2$Agemonths,sd)[as.character(temp2$Agemonths)]

#temp2 <- subset(temp2,Whodunnit != 'EAF')
temp2 <- subset(temp2,!is.na(Agemonths))
temp2 <- subset(temp2,Agemonths>10)

temp2$obs <- c(1:nrow(temp2))

summary(glmer(SurvivedNext~RTL+Agemonths+(1|BirdID)+(1|obs),data=temp2,family = 'binomial',control = glmerControl(optimizer = "bobyqa")))
summary(glm(SurvivedNext~RTL+Agemonths,data=temp2,family = 'binomial'))

ggplot(temp2,aes(y = RTL,x = Agemonths,col = factor(SurvivedNext)))+
  geom_point()+
  stat_smooth()
x <- tapply(temp2$RTL,list(temp2$SurvivedNext,factor(temp2$Agemonths)),mean)[,1:10]
plot(x[1,],type = 'l')
points(x[2,],type = 'l',lty = 2)

#Run the model
lm2 <- lmer(RTL ~  LogAge+Tarsus + Helper + NonHelper + Sex + BodyMass  +yday + (1|FieldPeriodID) + (1|BirdID) + (1|TerritoryID),
            data = temp,
            REML = FALSE)
lm2 <- standardize(lm2)
#Model averaging

summary(lm2)
confint.merMod(lm2)

lm3 <- dredge(lm2)
lm3 <- subset(lm3,delta <=6)
lmavg <- model.avg(lm3,fit=T)
myimp <- importance(lmavg) #Relative importance of each explanatory variable

@@

temp <- subset(dd3,Agemonths<12)
temp[,'Age (months)'] <- factor(temp$Agemonths)

>>>>

temp <- subset(dd,LayYear>1995)
temp$JA <- ifelse(temp$Ageclass == 'A','Adults','Juveniles')

@@

@@

temp <- subset(dd,!is.na(Insect))
temp$LogAge <- log(temp$Agemonths+1)

#Run the model
lm2 <- lmer(RTL ~  LogAge+Tarsus + Helper + NonHelper + Sex + BodyMass  +yday + Insect + Density + (1|LayYear) + (1|BirdID) + (1|TerritoryID),
            data = temp,
            REML = FALSE)
lm2 <- standardize(lm2)

#Model averaging
lm3 <- dredge(lm2)
lm3 <- subset(lm3,delta <=6)
lmavg <- model.avg(lm3,fit=T)
myimp <- importance(lmavg) #Relative importance of each explanatory variable

@@

temp <- dd3
temp[,'Age (months)'] <- factor(temp$Agemonths)
